---
title: "Project"
output:
  html_document:
    df_print: paged
---
# Setup
```{r}

library(openxlsx)
library(janitor)
library(tseries)
library(matlib)
library(fGarch)
library(quadprog)
library(boot)
library(MASS)
library(openxlsx)
par(mar=c(1,1,1,1))

#Import historical asset prices
#data = read.xlsx('Data.xlsx',colNames = TRUE)
data= read.xlsx("C:/Users/aishw/OneDrive/Desktop/OldDesktop/Desktop/Project-Stats/Data_M.xlsx",colNames=TRUE)
data = ts(data[,-1],start=c(2004,11),end=c(2019,11),frequency=12)
n = dim(data)[1]
#Import risk-free rate
rfr=read.xlsx('TB3MS.xlsx',colNames = TRUE)
rfr=ts(rfr[,-1]*0.01,start=c(2004,11),end=c(2019,11),frequency=12)
rfr_ave=mean(rfr[-1])
mu_rfr = rfr_ave/12
```

# 2. Descriptive Statistics
```{r}
#Setup
#Monthly Historical Returns
returns = (data[2:n,] / data[1:(n-1),] - 1)
colnames(returns) = c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R")
returns = ts(returns,start=c(2004,12),end=c(2019,11),frequency=12)
mean_vect = colMeans(returns) #Monthly return mean
cov_mat = cov(returns) #Monthly return covariance matrix
sd_vect = sqrt(diag(cov_mat)) #Monthly return SD
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
  print(i)
  print(skewness(returns[,i]))
  print(kurtosis(returns[,i],method="excess"))
}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
  print(min(returns[,i]))
}
```

## Monthly Price plots
```{r}
for (i in c("BRKB_AC","JPM_AC","JNJ_AC","PG_AC","XOM_AC","T_AC","BAC_AC","DIS_AC","INTC_AC","UNH_AC","VZ_AC","CVX_AC","PFE_AC","MRK_AC","WFC_AC"))
{plot(data[,i],ylab=i)}
```

## Monthly Return plots
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{plot(returns[,i],type="l",ylab=i)}
```

## Equity Curve plots
```{r}
for (i in c("BRKB_AC","JPM_AC","JNJ_AC","PG_AC","XOM_AC","T_AC","BAC_AC","DIS_AC","INTC_AC","UNH_AC","VZ_AC","CVX_AC","PFE_AC","MRK_AC","WFC_AC"))
{
  EQ_stock=data[,i]/data[,i][1]
  EQ_index=data[,"SP500_AC"]/data[,"SP500_AC"][1]
  y_min=min(c(min(EQ_stock),min(EQ_index)))
  y_max=max(c(max(EQ_stock),max(EQ_index)))
  plot(EQ_stock,ylab="Equity Curve ($)",col="blue",ylim=c(y_min,y_max))
 lines(data[,"SP500_AC"]/data[,"SP500_AC"][1],col="red")
 legend(2005,y_max,legend=c(i,"S&P 500"),col=c("blue","red"),lty=c(1,1),lwd=c(2.5,2.5))
 }
```

## Histograms for Returns
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{hist(returns[,i],xlab=i, main = paste("Histogram of",i))}
```

## Boxplots for Returns
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{boxplot(returns[,i],main=paste("Boxplot of",i))}
```

## QQ-plots for Returns
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{qqnorm(returns[,i],datax=T,main=paste("Boxplot of",i))
  qqline(returns[,i],datax=T)}
```

## Test for Normality
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{
  shapiro.test(returns[,i])
}
```

## Tests for Stationarity
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{print(kpss.test(returns[,i], null="Trend"))
  print(i)}
```

## Fitting different distributions
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
t.fit=stdFit(returns[,i])
  print(paste(i, "t Fit"))
  print(paste("AIC =",2*t.fit$objective+2*3))
  print(paste("BIC =",2*t.fit$objective+3*log(180)))
  print(t.fit$par)
  
st.fit=sstdFit(returns[,i])
  print(paste(i, "skewed t Fit"))
  print(paste("AIC =",2*st.fit$minimum+2*4))
  print(paste("BIC =",2*st.fit$minimum+4*log(180)))
  print(st.fit$estimate)

ged.fit=gedFit(returns[,i])
  print(paste(i, "GED Fit"))
  print(paste("AIC =",2*ged.fit$objective+2*3))
  print(paste("BIC =",2*ged.fit$objective+3*log(180)))
  print(ged.fit$par)

sged.fit=sgedFit(returns[,i])
  print(paste(i, "skewed GED Fit"))
  print(paste("AIC =",2*sged.fit$objective+2*4))
  print(paste("BIC =",2*sged.fit$objective+4*log(180)))
  print(sged.fit$par)
}
```

## Annualize
```{r}
ann_returns_mean=mean_vect*12 #annualized mean return
print(ann_returns_mean)
ann_returns_sd=sd_vect*sqrt(12) #annualized return SD
print(ann_returns_sd)
```

## Sharpe's slope for individual assets
```{r}
sharpe_ratio=(mean_vect-rfr_ave/12)/sd_vect
print(sharpe_ratio)
```

## Pairwise Scatterplot
```{r}
plot(as.data.frame(returns[,-16]))
```

## Beta
```{r}
ExReturns=returns-rfr[-1]/12 #excess return
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R"))
{
print(i)
print(summary(lm(ExReturns[,i]~ExReturns[,16]))$coef)
}
```

# 3. Portfolio Theory
## Short sale allowed
### MVP
```{r}
mu = matrix(mean_vect[1:15],
            nrow=15,ncol=1) #mu
names(mu) = c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R")
Omega = matrix(cov_mat[1:15,1:15],
               nrow=15,ncol=15) #covariance matrix
One = matrix(c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1),
             nrow=15,ncol=1)
#find weight across assets for MVP
w_mvp = (inv(Omega) %*% One)/as.numeric(t(One) %*% inv(Omega) %*% One)
#find mu_mvp
mu_mvp = t(w_mvp) %*% mu #mean return of MVP portfolio
#find sigma^2_mvp
var_mvp = t(w_mvp) %*% Omega %*% w_mvp 
#find sigma_mvp
sd_mvp=sqrt(var_mvp) #standard deviation of MVP portfolio
#annualized mean and sd
mu_mvp_ann = mu_mvp*12
sd_mvp_ann = sd_mvp*sqrt(12)
```

```{r}
# 5% VaR with $100,000 investment
return_mat=matrix(returns[,-16],nrow=180,ncol=15)
return_mvp=t(t(w_mvp) %*% t(return_mat))
VaR_mvp1 = quantile(return_mvp,0.05)*100000*(-1)
#ES
ES_mvp1 = -100000*sum(return_mvp[-return_mvp> -quantile(return_mvp,0.05)])/sum(as.numeric(-return_mvp>-quantile(return_mvp,0.05)))

#Bootstrap for SD and CI of VaR and ES
VaRES = function(x,i)
{
  q<-quantile(x[i],0.05)
  c(-q*100000,-mean(x[x<q])*100000)
}

res = boot(return_mvp,statistic=VaRES,R=10000,stype = "i")

print(paste("VaR",quantile(return_mvp,0.05)*(-100000)))
print(paste("ES",mean(return_mvp[return_mvp<quantile(return_mvp,0.05)])*(-100000)))
print(res)

print("CI of VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI of ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))

#5%VaR with $100000 investment (assume normal distribution)
VaR_mvp2 = -100000*(mu_mvp+sd_mvp*qnorm(0.05))
ES_mvp2 = 100000*(-mu_mvp+sd_mvp*(dnorm(qnorm(0.05))/0.05))

#Bootstrap for SD and CI of VaR and ES
VaRES2 = function(x,i)
{
  fit.norm = fitdistr(x[i],"normal")
  mu.norm = fit.norm$estimate[["mean"]]
  sd.norm=fit.norm$estimate[["sd"]]
  VaR.norm = -100000*(mu.norm+sd.norm*qnorm(0.05))
  ES.norm = 100000*(-mu.norm+sd.norm*(dnorm(qnorm(0.05))/0.05))
  return(c(VaR.norm,ES.norm))
}

res2=boot(return_mvp,statistic = VaRES2, R=10000,stype = "i")
print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

### 6% return per year using only risky assets
```{r}
mu_0.005=0.005 #target monthly return
w1 = inv(Omega) %*% One/as.numeric(t(One) %*% inv(Omega) %*% One)
w2 = inv(Omega) %*% mu/as.numeric(t(One) %*% inv(Omega) %*% mu)
delta_w=w1-w2
e1 = (as.numeric(t(w1)%*%mu)*w2-as.numeric(t(w2) %*% mu)*w1)/as.numeric(t(mu) %*% delta_w)
e2 = (w1-w2)/as.numeric(t(mu) %*% delta_w)
w_efficient=e1+mu_0.005*e2
print(w_efficient) #weight of 6% return per year using only risky assets

var_efficient = t(w_efficient) %*% Omega %*% w_efficient
sd_efficient = sqrt(var_efficient) #monthly risk
print(sd_efficient)
print(sqrt(12)*sd_efficient) #annualized risk

mu_efficient = t(w_efficient) %*% mu
print(as.numeric(mu_efficient)) #monthly return
print(12*mu_efficient) #annualized return

#5%VaR with $100000 investment
return_efficient=t(t(w_efficient) %*% t(return_mat))
VaR_efficient1 = quantile(return_efficient,0.05)*100000*(-1)
print(VaR_efficient1)
#ES
ES_efficient1 = -100000*sum(return_efficient[-return_efficient> -quantile(return_efficient,0.05)])/sum(as.numeric(-return_efficient>-quantile(return_efficient,0.05)))
print(ES_efficient1)

#bootstrap
res = boot(return_efficient,statistic=VaRES,R=10000,stype = "i")
print(paste("VaR",quantile(return_efficient,0.05)*(-100000)))
print(paste("ES",mean(return_efficient[return_efficient<quantile(return_efficient,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))

#5%VaR with $100000 investment (assume normal distribution)
VaR_efficient2 = -100000*(mu_efficient+sd_efficient*qnorm(0.05))
ES_efficient2 = 100000*(-mu_efficient+sd_efficient*(dnorm(qnorm(0.05))/0.05))

res2=boot(return_efficient,statistic = VaRES2, R=10000,stype = "i")
print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

### Tangency portfolio
```{r}
w_tangency=(inv(Omega) %*% (mu-mu_rfr*One))/as.numeric(t(One) %*% inv(Omega) %*% (mu-mu_rfr*One))
print(w_tangency) #weight in tangency portfolio
mu_tangency = t(w_tangency) %*% mu #monthly return
var_tangency = t(w_tangency) %*% Omega %*% w_tangency
sd_tangency = sqrt(var_tangency) #monthly risk
sharpe_tangency=(mu_tangency-mu_rfr)/sd_tangency #sharpe ratio of tangency portfolio

#5%VaR with $100000 investment
return_tangency=t(t(w_tangency) %*% t(return_mat))
VaR_tangency1 = quantile(return_tangency,0.05)*100000*(-1)
print(VaR_tangency1)
#ES
ES_tangency1 = -100000*sum(return_tangency[-return_tangency> -quantile(return_tangency,0.05)])/sum(as.numeric(-return_tangency>-quantile(return_tangency,0.05)))
print(ES_tangency1)

#bootstrap
res = boot(return_tangency,statistic=VaRES,R=10000,stype = "i")
print(paste("VaR",quantile(return_tangency,0.05)*(-100000)))
print(paste("ES",mean(return_tangency[return_tangency<quantile(return_tangency,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))

#5%VaR with $100000 investment (assume normal distribution)
VaR_tangency2 = -100000*(mu_tangency+sd_tangency*qnorm(0.05))
ES_tangency2 = 100000*(-mu_tangency+sd_tangency*(dnorm(qnorm(0.05))/0.05))

res2=boot(return_tangency,statistic = VaRES2, R=10000,stype = "i")
print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

### 6% return with T-bills and Tangency portfolio
```{r}
theta=(0.005-as.numeric(mu_tangency))/(mu_rfr-as.numeric(mu_tangency))
print(theta) #weight to T-bills
mu_mixed = theta*mu_rfr+(1-theta)*as.numeric(mu_tangency)
print(mu_mixed)
print(mu_mixed*12)
var_tangency = t(w_tangency) %*% Omega %*% w_tangency
var_mixed = (1-theta)^2*as.numeric(var_tangency)
sd_mixed = sqrt(var_mixed)
print(sd_mixed)
print(sd_mixed*sqrt(12))

# 5%VaR with $100000 investment (nonparametric)
return_mixed=t(t((1-theta)*w_tangency) %*% t(return_mat)+theta*mu_rfr)
VaR_mixed1 = quantile(return_mixed,0.05)*100000*(-1)
print(VaR_mixed1)
#ES
ES_mixed1 = -100000*sum(return_mixed[-return_mixed> -quantile(return_mixed,0.05)])/sum(as.numeric(-return_mixed>-quantile(return_mixed,0.05)))
print(ES_mixed1)

#bootstrap
res = boot(return_mixed,statistic=VaRES,R=10000,stype = "i")
print(paste("VaR",quantile(return_mixed,0.05)*(-100000)))
print(paste("ES",mean(return_mixed[return_mixed<quantile(return_mixed,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))

#5%VaR with $100000 investment (assume normal distribution)
VaR_mixed2 = -100000*(mu_mixed+sd_mixed*qnorm(0.05))
ES_mixed2 = 100000*(-mu_mixed+sd_mixed*(dnorm(qnorm(0.05))/0.05))

#bootstrap
res2=boot(return_mixed,statistic = VaRES2, R=10000,stype = "i")
print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

### Efficient Frontier
```{r}
M=length(mean_vect[1:15])
Amat = cbind(rep(1,M),mean_vect[1:15])
muP = seq(0.003, 0.016, length = 300)
sdP = muP # set up storage for std dev’s of portfolio returns
weights = matrix(0, nrow = 300, ncol = M) # storage for weights
for (i in 1:length(muP))
{
  bvec = c(1, muP[i])
  result = solve.QP(Dmat = 2 * cov_mat[1:15,1:15], dvec = rep(0, M),
                    Amat = Amat, bvec = bvec, meq = 2)
  sdP[i] = sqrt(result$value)
  weights[i,] = result$solution
}
plot(sdP,muP,type="l",xlim=c(0,0.05),ylim=c(0.001,.016))
points(0,mu_rfr,pch=15)
sharpe =(muP-mu_rfr)/sdP
ind = (sharpe == max(sharpe))
lines(c(0,sdP[ind]),c(mu_rfr,muP[ind]),col="red",lwd=3)
points(sdP[ind],muP[ind],pch=15)
ind2 = (sdP == min(sdP))
points(sdP[ind2],muP[ind2],pch=17)
ind3 = (muP > muP[ind2])
lines(sdP[ind3],muP[ind3],type="l",xlim=c(0,.05),ylim=c(0,.02),col="cyan",lwd=3)
legend("topleft",c("efficient frontier","efficient portfolios"),
lty=c(1,1),
lwd=c(3,3),
pch=c("",""),
col=c("cyan","red"),
)
```

## Short sale not allowed
### Efficient Frontier
```{r}
M=length(mean_vect[1:15])
Amat = cbind(rep(1,M),mean_vect[1:15],diag(1,nrow=M))
muP = seq(min(mean_vect[1:15]),max(mean_vect[1:15]), length = 300)
sdP = muP # set up storage for std dev’s of portfolio returns
weights = matrix(0, nrow = 300, ncol = M) # storage for weights
for (i in 1:length(muP))
{
  bvec = c(1, muP[i],rep(0,M))
  result = solve.QP(Dmat = 2 * cov_mat[1:15,1:15], dvec = rep(0, M),
                    Amat = Amat, bvec = bvec, meq = 2)
  sdP[i] = sqrt(result$value)
  weights[i,] = result$solution
}
plot(sdP,muP,type="l",xlim=c(0,0.08),ylim=c(0.001,.016))
points(0,mu_rfr,pch=15)
sharpe =(muP-mu_rfr)/sdP
ind = (sharpe == max(sharpe))
lines(c(0,sdP[ind]),c(mu_rfr,muP[ind]),col="red",lwd=3)
points(sdP[ind],muP[ind],pch=15)
ind2 = (sdP == min(sdP))
points(sdP[ind2],muP[ind2],pch=17)
ind3 = (muP > muP[ind2])
lines(sdP[ind3],muP[ind3],type="l",xlim=c(0,.08),ylim=c(0,.02),col="cyan",lwd=3)
legend("topleft",c("efficient frontier","efficient portfolios"),
lty=c(1,1),
lwd=c(3,3),
pch=c("",""),
col=c("cyan","red"),
)
```

###MVP
```{r}
ind2 = (sdP == min(sdP))
n_w_mvp=weights[ind2,]
#find mu_mvp
n_mu_mvp = t(n_w_mvp) %*% mu #mean return
#find sigma^2_mvp
n_var_mvp = t(n_w_mvp) %*% Omega %*% n_w_mvp
#find sigma_mvp
n_sd_mvp=sqrt(n_var_mvp) #standard deviation
#annualized mean and sd
n_mu_mvp_ann = n_mu_mvp*12
n_sd_mvp_ann = n_sd_mvp*sqrt(12)
print(n_mu_mvp)

# 5% VaR with $100,000 investment
n_return_mvp=t(t(n_w_mvp) %*% t(return_mat))
n_VaR_mvp1 = quantile(n_return_mvp,0.05)*100000*(-1)
print(n_VaR_mvp1)
#ES
n_ES_mvp1 = -100000*sum(n_return_mvp[-n_return_mvp> -quantile(n_return_mvp,0.05)])/sum(as.numeric(-n_return_mvp>-quantile(n_return_mvp,0.05)))
print(n_ES_mvp1)

res = boot(n_return_mvp,statistic=VaRES,R=10000,stype = "i")

print(paste("VaR",quantile(n_return_mvp,0.05)*(-100000)))
print(paste("ES",mean(n_return_mvp[n_return_mvp<quantile(n_return_mvp,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))
#5%VaR with $100000 investment (assume normal distribution)
n_VaR_mvp2 = -100000*(n_mu_mvp+n_sd_mvp*qnorm(0.05))
n_ES_mvp2 = 100000*(-n_mu_mvp+n_sd_mvp*(dnorm(qnorm(0.05))/0.05))

res2=boot(n_return_mvp,statistic = VaRES2, R=10000,stype = "i")

print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

### 6% Risky Asset
Cannot be reached here because min(mean_vect)>0.005

### Tangency portfolio
```{r}
n_w_tangency = weights[ind,] #weights of Tangency Portfolio
n_mu_tangency = t(n_w_tangency) %*% mu
n_var_tangency = t(n_w_tangency) %*% Omega %*% n_w_tangency
n_sd_tangency = sqrt(n_var_tangency) #monthly risk
n_sharpe_tangency=(n_mu_tangency-mu_rfr)/n_sd_tangency #sharpe ratio of tangency portfolio
print(n_mu_tangency*12) #annualized return
print(n_sd_tangency*sqrt(12)) #annualized risk

#5%VaR with $100000 investment (nonparametric)
n_return_tangency=t(t(n_w_tangency) %*% t(return_mat))
n_VaR_tangency1 = quantile(n_return_tangency,0.05)*100000*(-1)
print(n_VaR_tangency1)
#ES
n_ES_tangency1 = -100000*sum(n_return_tangency[-n_return_tangency> -quantile(n_return_tangency,0.05)])/sum(as.numeric(-n_return_tangency>-quantile(n_return_tangency,0.05)))
print(n_ES_tangency1)

#bootstrap
res = boot(n_return_tangency,statistic=VaRES,R=10000,stype = "i")
print(paste("VaR",quantile(n_return_tangency,0.05)*(-100000)))
print(paste("ES",mean(n_return_tangency[n_return_tangency<quantile(n_return_tangency,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))

#5%VaR with $100000 investment (assume normal distribution)
n_VaR_tangency2 = -100000*(n_mu_tangency+n_sd_tangency*qnorm(0.05))
n_ES_tangency2 = 100000*(-n_mu_tangency+n_sd_tangency*(dnorm(qnorm(0.05))/0.05))

res2=boot(n_return_tangency,statistic = VaRES2, R=10000,stype = "i")
print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```
### 6% Tangency + Risk-Free
```{r}
n_theta=(0.005-as.numeric(n_mu_tangency))/(mu_rfr-as.numeric(n_mu_tangency))
n_mu_mixed = n_theta*mu_rfr+(1-n_theta)*as.numeric(n_mu_tangency)
print(n_mu_mixed)
print(n_mu_mixed*12)
n_var_tangency = t(n_w_tangency) %*% Omega %*% n_w_tangency
n_var_mixed = (1-n_theta)^2*as.numeric(n_var_tangency)
n_sd_mixed = sqrt(n_var_mixed)
print(n_sd_mixed)
print(n_sd_mixed*sqrt(12))
#5%VaR with $100000 investment (nonparametric)
n_return_mixed=t(t((1-n_theta)*n_w_tangency) %*% t(return_mat)+n_theta*mu_rfr)
n_VaR_mixed1 = quantile(n_return_mixed,0.05)*100000*(-1)
print(n_VaR_mixed1)
#ES
n_ES_mixed1 = -100000*sum(n_return_mixed[-n_return_mixed> -quantile(n_return_mixed,0.05)])/sum(as.numeric(-n_return_mixed>-quantile(n_return_mixed,0.05)))
print(n_ES_mixed1)

res = boot(n_return_mixed,statistic=VaRES,R=10000,stype = "i")

print(paste("VaR",quantile(n_return_mixed,0.05)*(-100000)))
print(paste("ES",mean(n_return_mixed[n_return_mixed<quantile(n_return_mixed,0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))
#5%VaR with $100000 investment (assume normal distribution)
n_VaR_mixed2 = -100000*(n_mu_mixed+n_sd_mixed*qnorm(0.05))
n_ES_mixed2 = 100000*(-n_mu_mixed+n_sd_mixed*(dnorm(qnorm(0.05))/0.05))

res2=boot(n_return_mixed,statistic = VaRES2, R=10000,stype = "i")

print(res2)

print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
```

# 5 Principal Component Analysis
```{r}
D=matrix(rep(0,15*15),nrow=15,ncol=15)
for (i in seq(1,15,1))
{D[i,i]=sd_vect[i]}
corr_return = inv(D) %*% cov_mat[1:15,1:15] %*% inv(D)
print(corr_return)
return.pca = prcomp(returns[,1:15])
summary(return.pca)
fact=factanal(returns[,1:15],factors=7,rotation="none",cutoff=0.05)
print(fact)
loadings = matrix(as.numeric(loadings(fact)), ncol = 7)
unique = as.numeric(fact$unique)
betas = t(loadings) 

Sigma_R_hat = t(betas) %*% betas + diag( unique, ncol=15)
#rotation
fact_rotation=factanal(returns[,1:15],factors=7)
print(fact_rotation)#
print(eigen(Sigma_R_hat-corr_return)$values)# eigenvalues of the difference of the estimate and sample correlation matrix 
```

# 6 Risk Managment
## VaR(0.05) Monthly & ES for assets
### nonparametric
```{r}
for (r in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
res = boot(returns[,r],statistic=VaRES,R=10000,stype = "i")

print(paste(r,"VaR",quantile(returns[,r],0.05)*(-100000)))
print(paste(r,"ES",mean(returns[,r][returns[,r]<quantile(returns[,r],0.05)])*(-100000)))
print(res)

print("CI VaR")
print(boot.ci(res,conf=0.95,,type="perc",index=1))
print("CI ES")
print(boot.ci(res,conf=0.95,,type="perc",index=2))
}

```
### parametric
```{r}
for (i in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
print(paste(i, "5% VaR (assume normal distribution)"))
print(-100000*(mean_vect[i]+sd_vect[i]*qnorm(0.05)))
print(paste(i, "ES (assume normal distribution)"))
print(100000*(-mean_vect[i]+sd_vect[i]*(dnorm(qnorm(0.05))/0.05)))
}

#Bootstrap
for (r in c("BRKB_R","JPM_R","JNJ_R","PG_R","XOM_R","T_R","BAC_R","DIS_R","INTC_R","UNH_R","VZ_R","CVX_R","PFE_R","MRK_R","WFC_R","SP500_R"))
{
res2=boot(returns[,r],statistic = VaRES2, R=10000,stype = "i")

print(res2)
print("CI VaR")
print(boot.ci(res2,conf=0.95,,type="norm",index=1))
print("CI ES")
print(boot.ci(res2,conf=0.95,,type="norm",index=2))
}
```
# 7 Copula
```{r}
library(copula)
library(sn)

Ct=fitCopula(copula=tCopula(dim=15),data=pobs(returns[,-16]),method="ml")
Ct@estimate
print(loglikCopula(param=Ct@estimate, u=pobs(returns[,-16]), copula=tCopula(dim = 15)))
LastValue=loglikCopula(param=Ct@estimate, u=pobs(returns[,-16]), copula=tCopula(dim = 15))
print(-2*LastValue + 2*length(Ct@estimate))

Cgauss = fitCopula(copula=normalCopula(dim = 15), data=pobs(returns[,-16]),method="ml")
print(Cgauss@estimate)

print(loglikCopula(param=Cgauss@estimate, u=pobs(returns[,-16]),copula=normalCopula(dim = 15)))
LastValue=loglikCopula(param=Cgauss@estimate, u=pobs(returns[,-16]),copula=normalCopula(dim = 15))
print(-2*LastValue + 2*length(Cgauss@estimate))

Cfr = fitCopula(copula=frankCopula(1, dim=15), data=pobs(returns[,-16]),method="ml")
print(Cfr@estimate)
print(loglikCopula(param=Cfr@estimate, u=pobs(returns[,-16]),copula=frankCopula(dim = 15)))
LastValue=loglikCopula(param=Cfr@estimate, u=pobs(returns[,-16]),copula=frankCopula(dim = 15))
print(-2*LastValue + 2*length(Cfr@estimate))

Ccl = fitCopula(copula=claytonCopula(1, dim=15), data=pobs(returns[,-16]),method="ml")
Ccl@estimate
print(loglikCopula(param=Ccl@estimate, u=pobs(returns[,-16]),copula=claytonCopula(dim = 15)))
LastValue=loglikCopula(param=Ccl@estimate, u=pobs(returns[,-16]),copula=claytonCopula(dim = 15))
print(-2*LastValue+ 2*length(Ccl@estimate))
```